%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-.05pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Joe Acanfora}} & Email : \href{mailto:joeaca04@gmail.com}{joeaca04@gmail.com}\\
  \href{}{} & Phone : 607.643.1262 \\
\end{tabular*}



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bank of America Merril Lynch}{New York, NY}
      {Quartz Application Developer}{Dec 2015 - Present}
      \resumeItemListStart
        \resumeSubItem{Project Background}
          {Quartz is a platform, built in python, for pricing trades, managing positions and computing risk exposures. Worked on the 'Sparck' project, whose goal is to calculate counter party credit risk for over the counter derivative trades made by the bank.}  
          \resumeSubItem{Contribution}{Responsibilities included implementing batch jobs to run on the distributed computing platform, known as ‘The Grid’, and assembling reports for business users of the platform.  Member of a global agile-scrum team that included locations in India and London. }
      \resumeItemListEnd

    \resumeSubheading
      {CapTech Ventures Inc.}{Richmond, VA}
      {Consultant}{June 2015 - Present}
      \resumeItemListStart
        \resumeItem{Bank of America Merril Lynch}
          {Full time travel on client site 5 days a week. See above for more details.}
        \resumeItem{Digital Refresh Project}
          {Worked on CapTech’s Digital Refresh Project, the firms’ effort to redesign www.captechconsulting.com using Sitecore and HTML5.  Worked on an agile team to implement a new blogging and content approval system for other consultants as well as brought new search functionality to the public view of the website. 
        }
      \resumeItemListEnd

    \resumeSubheading
      {Virginia Tech}{Blacksburg, VA}
      {Student leader}{August 2014 - May 2015}
      \resumeItemListStart
        \resumeItem{Virginia Tech Innovate Living Learning Community Senior Resident Member}
          {Teaching Assistant for the fundamentals of entrepreneurship course.
            Community leadership position to help students matriculate.}
        \resumeItem{Research Assistant - Pamplin College of Business}
          {Built a web application in python that scraped data on Kickstarter projects and allowed users to code data for further analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {Avid Aerospace LLC}{Blacksburg, VA}
      {Software Developer Intern}{May 2013 -  March 2015}
      \resumeItemListStart
        Contributed to a suite of Aerospace design applications in C++ using the Qt framework. Work included design and development of GUI elements that followed Model-View architecture patterns that fit into a large existing code base. An example element I developed was the implementation of a singleton global user-selectable widget that updated all of the measurement units in Avid’s visual airfoil design program.  Participated in code review using Git and Gerrit and design meeting with the software development team. 
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Virginia Tech}{Blacksburg, VA}
      {Bachelor of Science in Computer Science}{May 2015}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{Java, Python, SQL, C++, R, C\#, Bash, HTML5}
      \resumeSubItem{Technologies}{Android, Hadoop, Flask, Git, Qt5, *Nix}
  \resumeSubHeadingListEnd

%-----------CERTS-----------------------
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubItem{Cloudera Certified Administrator for Apache Hadoop (CCA-500)}
      {certification proves that I have demonstrated the technical knowledge, skills, and ability to configure, deploy, maintain, and secure an Apache Hadoop cluster.}
  \resumeSubHeadingListEnd
  
%----------Awards and Recognitions-----
\section{Awards and Recognitions}
  \resumeSubHeadingListStart
    \resumeItem{2014 VT Knowledgeworks Student Concept Business Challenge}
      { 1st place representing Team Vestigo, included a \$10k Scholarship.}
     \resumeItem{APEX Center for Innovation and Entrepreneurship 2015 Trailblazer award} {for excellence in entrepreneurial involvement at Virginia Tech.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
